Manuscript results: Forecasting influenza using ARIMA and ARIMAX

### 2025-05-23 manuscript_results.Rmd
update

ggsave(model_improv, height = 4.5, width = 9,  filename="Fig10.jpg")  
```
hospitalizations

@@

# Save the combined plot
ggsave("Fig10.png", combined_plot, width = 7, height = 7, dpi = 600)

>>>>

#ggsave(model_improv, height = 4.5, width = 9,  filename="Fig10.jpg")  
```
hospitalizations

@@

# Save the combined plot
ggsave("Fig10.jpg", combined_plot, width = 7, height = 7, dpi = 600)
